% ===============================================
% Author: Richie Zhou
% Description: Computer Science Resume Template
% ===============================================

%-------------------- Packages --------------------
\documentclass[letterpaper,11pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}

%-------------------- Font Options --------------------
\usepackage{times}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

% Set margins
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------- Custom commands --------------------
\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-4pt}}
  }
}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-4pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small{#2}} \\
      \small{#3} & \small{#4} \\
    \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
}

\newcommand{\resumeSubItem}[1]{%
  \resumeItem{#1}%
  \vspace{-4pt}%
}


\newcommand{\resumeSubHeadingListStart}{%
  \begin{itemize}[leftmargin=0.0in, label={}]%
}

\newcommand{\resumeSubHeadingListEnd}{%
  \end{itemize}%
  \vspace{-10pt}%
}

\newcommand{\resumeProjectHeading}[2]{%
  \vspace{-2pt}\item%
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}%
    \small{#1} & \small{#2}\\%
  \end{tabular*}%
  \vspace{-8pt}%
}

\newcommand{\resumeItemListStart}{%
  \begin{itemize}%
}

\newcommand{\resumeItemListEnd}{%
  \end{itemize}%
  \vspace{-8pt}%
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% ==================== Resume Starts Here ====================
\begin{document}
  %-------------------- Heading --------------------
  \begin{center}
    {\Large \textbf{Yujian (Richie) Zhou}} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 6466234317 ~ \href{mailto:richiezhouyjz@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ {richiezhouyjz@gmail.com}}
    \href{https://www.linkedin.com/in/richiezhou/}{\raisebox{-0.2\height}\faLinkedin\ {linkedin.com/in/richiezhou/}}
    \href{https://arunike.github.io/}{\raisebox{-0.2\height}\faGithub\ {arunike.github.io/}}
  \end{center}
  \vspace{-20pt}

  %-------------------- Education --------------------
  \section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
            {TBD\vspace{-3pt}}{TBD}
            {Master of Science in Computer Science}{Sep. 2024 -- May 2025}
            \vspace{-3pt}
        \resumeSubheading
            {University of Wisconsin - Madison\vspace{-3pt}}{Madison, WI}
            {Bachelor of Science in Computer Science}{Sep. 2020 -- Dec. 2023}
    \resumeSubHeadingListEnd
  \vspace{-5pt}

  %-------------------- Experience --------------------
  \section{Experience}
    \resumeSubHeadingListStart
      \resumeSubheading
        {Software Engineer Intern, Northern Trust\vspace{-3pt}} {Chicago, IL}
        {June 2023 -- August 2023} {}
        \resumeItemListStart
          \resumeItem{Developed and optimized algorithms in \textbf{Java and C++} to enhance the computational efficiency of NT's Goals Driven Wealth Management platform, leading to an 8\% increase in transaction processing speed.}
          \resumeItem{Implemented and fine-tuned \textbf{RESTful APIs using Spring Boot} for efficient data communication within investment reporting trade model microservices, achieving a 15\% enhancement in system responsiveness.}
          \resumeItem{Conducted quantitative analysis and applied statistical techniques in \textbf{C++} to optimize cloud-based services, resulting in improved system reliability and a 12\% increase in uptime.}
          \resumeItem{Architected and executed complex \textbf{SQL queries and data models in Snowflake}, leveraging advanced data analysis and processing skills to accelerate data extraction for investment reporting by 30\%, supporting swift data-driven decisions.}
        \resumeItemListEnd

      \resumeSubheading
        {Software Developer Intern, Rockitcoin\vspace{-3pt}} {Chicago, IL}
        {August 2022 -- March 2023} {}
        \resumeItemListStart
          \resumeItem{Revamped Rockitcoin's user authorization interface for mobile and web platforms using \textbf{TypeScript with React}, elevating security and usability, resulting in a 20\% increase in user retention rate.}
          \resumeItem{Designed intuitive user interfaces for a user base of over 8,000 using \textbf{TypeScript with React}, focusing on user-friendly design and efficient real-time data interaction, leading to a 35\% improvement in user satisfaction.}
          \resumeItem{Improved UI rendering speed by 10\% through debouncing in \textbf{React}, effectively limiting API requests from text fields.}
          \resumeItem{Adopted \textbf{HashMap} data structures for efficient frontend user data management, achieving a 20\% improvement in data retrieval speeds. }
      \resumeItemListEnd

      \resumeSubheading
        {Full Stack Developer Developer Intern, UNFCU\vspace{-3pt}} {New York, NY}
        {May 2022 -- August 2022} {}
        \resumeItemListStart
          \resumeItem{Enhanced the dynamic saving rate recommendation page using \textbf{JavaScript, HTML, CSS, and PHP}, boosting savings account enrollment by 3\%.}
          \resumeItem{Utilized the \textbf{Next.js} framework to architect and deploy intuitive entry pages, streamline navigation, and cohesively convey company culture, culminating in a measurable 30\% uplift in customer satisfaction rate.}
          \resumeItem{Implemented \textbf{Python} scripts to automate loan document data extraction, enabling efficient keyword retrieval and streamlining team operations, leading to a 30\% faster deployment cycle.}
          \resumeItem{Maintained \textbf{SQL} databases with over 150,000+ entries, creating an infrastructure for real-time reporting of key metrics like customer satisfaction, annual revenues, and sales retention rates, providing valuable insights to stakeholders.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd
  \vspace{-5pt}

  %-------------------- Project --------------------
  \section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{\href{https://github.com/arunike/Weather-Stream-Analytic} {Weather Stream Analytic}}} {Nov. 2023}
        \resumeItemListStart
          \resumeItem{Implemented a \textbf{Kafka producer} for data ingestion from weather stations and a \textbf{Kafka consumer} with exactly one message processing to ensure data integrity for web dashboard summaries.}
          \resumeItem{Utilized \textbf{Spark} Streaming for real-time data processing, generating datasets for ML applications in weather forecasting.}
          \resumeItem{Maintaining data accuracy and developing predictive models for weather analysis, leveraging \textbf{Spark's} capabilities for dynamic temperature averaging and forecast modeling.}
        \resumeItemListEnd
            
      \resumeProjectHeading
        {\textbf{\href{https://github.com/arunike/Five-Course-Bird-Feeder-Frontend} {Five Course Bird Feeder}}} {Spring 2023}
        \resumeItemListStart
          \resumeItem{Developed a responsive front-end Interface using \textbf{TypeScript with React}, fascinating user interactions through live and recorded video streaming of the user's bird feeder.}
          \resumeItem{Implemented a versatile backend \textbf{Spring Boot API} supporting dynamic bird feeding schedules, user profile management, and real-time streaming of bird feeder cameras, enhancing user engagement and interactive experience.}
          \resumeItem{Integrated ML and image labeling techniques using \textbf{Python (Tensorflow)} to analyze bird visitation patterns, generating insightful statistics on bird species, frequency of visits, and visitation times displayed through interactive graphs and tables.}
        \resumeItemListEnd 
          
      \resumeProjectHeading
      {\textbf{\href{https://github.com/arunike/} {Online Shop}}} {Summer 2022}
      \resumeItemListStart
        \resumeItem{Developed an intuitive online shopping platform using \textbf{Spring Boot}, enhancing the shopping experience for users.}
        \resumeItem{Utilized the \textbf{Redis} in-memory data structure to facilitate real-time product search and optimize shopping cart functionality.}
        \resumeItem{Modified the \textbf{JavaScript API} to streamline communication between buyers and sellers, improving transaction processing.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd
  \vspace{-5pt}
  
  %-------------------- Skills --------------------
  \section{Technical Skills}
    \begin{itemize}[leftmargin=0.00in, label={}]
        \small{\item{
          \textbf{Programming Languages:} {Java, C/C++, Python, R, SQL, JavaScript, TypeScript} \\
          \textbf{Frameworks and Libraries:} {React, Vue, Spring Boot} \\
          \textbf{Tools and Technologies:} {HTML, CSS, Cassandra, Kafka, Spark, Snowflake, Firebase, Redis, NodeJS, Docker, Kotlin} \\
        }}
    \end{itemize}
\end{document}
